Full-depth Coadds of the WISE and First-year NEOWISE-Reactivation Images

### 2016-03-04 ms.tex
add full DESI funding acknowledgment

This research used resources of the National Energy Research Scientific 
Computing Center, a DOE Office of Science User Facility supported by the Office
of Science of the U.S. Department of Energy under Contract No. 
DE-AC02-05CH11231.

This research made use of the NASA Astrophysics Data System (ADS) and the IDL 
Astronomy User's Library at Goddard. \footnote{Available at 
\texttt{http://idlastro.gsfc.nasa.gov}}

>>>>

This research is supported by the Director, Office of Science, Office of High 
Energy Physics of the U.S. Department of Energy under Contract No. 
DE–AC02–05CH1123, and by the National Energy Research Scientific Computing 
Center, a DOE Office of Science User Facility under the same contract; 
additional support for DESI is provided by the U.S. National Science
Foundation, Division of Astronomical Sciences under Contract No. AST-0950945 to
the National Optical Astronomy Observatory; the Science and Technologies 
Facilities Council of the United Kingdom; the Gordon and Betty Moore 
Foundation; the Heising-Simons Foundation; and by the DESI Member Institutions.

This research made use of the NASA Astrophysics Data System (ADS) and the IDL 
Astronomy User's Library at Goddard.\footnote{Available at 
\texttt{http://idlastro.gsfc.nasa.gov}}
